---
title: "San Nic Jan 2020"
author: "Jan Walker"
date: "9/11/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

#Load

These are the common packages I always load.

```{r Packages}

library(nlme)
library(ggplot2)
library(car)
library(plotrix)
library(ez)
library(vegan)
library(cowplot)
library(gridExtra)
library(HH)
library(lme4)

#Gams

library(mgcv)

library(viridis)
#install.packages("dplyr")

#detach(package:dplyr )
library(dplyr)
#install.packages("tidyr")
#detach(package:tidyr)
library(tidyr)
library(mvtnorm)
library(statmod)

library(MASS)

#install.packages("lmerTest")
library(fitdistrplus)
library(lmerTest)

#install.packages("pander")
library(pander)
library(magrittr)

#install.packages("metafor") - for LRR
library(metafor) 

#PCA
library(car)
#install.packages(c("corrplot","psych", "caret"))
library(psych)
library(corrplot)
library(caret)
#install.packages("bootstrap")
library(bootstrap)

#install.packages("npmv")
library(npmv)
#install.packages("ggfortify")
library(ggfortify)
#install.packages("ggrepel")
library(factoextra)
library(ggrepel) #https://cran.mtu.edu/web/packages/ggrepel/vignettes/ggrepel.html

#library ggfortify https://terrytangyuan.github.io/2018/02/12/autoplotly-intro/ 


```

```{r Clear}

#To clear the environment

ls()
rm(list=ls()) 

```

```{r Colors}

#These are the colors we'll use throughout. This is no run-able code, but more of a place-holder and a reminder.

#I also like to use color-blind friendly palettes

#http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/

#Teg = Grey  
"#999999"

#Herm = Blue 
"#56B4E9"

#Ab = Black
"#000000"

#Ab/Urchin= Green
"#009E73"

```


All of the below surveys are from San Nic in January 2020

#Wrack Surveys

These were the wrack focused surveys, mainly taken by Jan, during the January trip to San Nic in 2020.



```{r Data}

 setwd("~/Desktop/R Data/SNI JAN 2020 Data")
Wrack_Survey_Data <- read.csv("WrackFocusedSurveySNIJan2020.csv")

```

##Composition

```{r Plots}

#create a dataframe with just important columns

Wrack_Survey_Data_reduced <- na.omit(Wrack_Survey_Data[, -c(1:4, 6, 8, 13)])

# Change data from wide to long format for  analyses
Wrack_Survey_Data_long <- gather(data = Wrack_Survey_Data_reduced, 
                                 key = "Species", value = "Abundance", ... 
                                 =  c(teg, herm, ab), factor_key = TRUE)
# Key is the new name for the category, value is the new name for the response (in this case Abundance), … = c() is a list of all the species you want to aggregate, factor_key = true makes Species a factor.

##### Abundance Plots

#rename habitats
levels(Wrack_Survey_Data_long$habitat)
levels(Wrack_Survey_Data_long$habitat) <- c("Abalone", "Tegula/Hermit") 

#rename species
levels(Wrack_Survey_Data_long$Species)
levels(Wrack_Survey_Data_long$Species) <- c("Tegula", "Hermit", "Abalone") 

###Stacked Bar Plot

 pdf(file = "Stackbarplot_wracksurvey_Jan2020SanNic.pdf", width= 6, height = 8, useDingbats=F)

ggplot(Wrack_Survey_Data_long, 
       aes(x=habitat, y=Abundance, fill = Species)) + 
  geom_bar(stat = "identity", position = "fill") + 
  ylab("Proportional Abundance") + 
  xlab("Habitat") + 
  scale_fill_manual(values=c("#999999", "#56B4E9",
                                "#000000")) +
  theme(axis.title.x = element_text(face="bold", size=22),
        axis.text.x  = element_text(size=20)) +
  theme(axis.title.y = element_text(angle=90, face="bold", 
                                    size=22, 
                                    vjust=1.2),
        axis.text.y  = element_text(size=20)) 
  
dev.off()

######Barplot

meanAbundance <- Wrack_Survey_Data_long %>% 
  group_by(habitat, Species) %>% 
  summarize(mean_Abundance = mean(Abundance), SE = std.error(Abundance))

pdf(file = "Barplot_wracksurvey_Jan2020SanNic.pdf", width = 6, height = 7, useDingbats=F)

Plot_Abundance_Bar <- ggplot(data=meanAbundance,
                      aes(y=mean_Abundance, 
                          x=habitat, 
                          fill = Species)) +
  geom_bar(stat = "identity", colour = "black", 
           position = position_dodge(width = 0.9))

Plot_Abundance_Bar + theme(axis.title.x = element_text(face="bold",
                                                 size=22),
                           axis.text.x  = element_text(size=20)) + 
  xlab("Habitat") +
  theme(axis.title.y = element_blank()) + 
  ylab("Abundance (# on wrack)") +
  theme(axis.title.y = element_text(angle=90, 
                                    face="bold", 
                                    size=22, 
                                    vjust=1.5),
        axis.text.y  = element_text(size=20)) +
  geom_errorbar(aes(ymin=mean_Abundance - SE, 
                    ymax=mean_Abundance + SE), width = 0.05,
                position=position_dodge(width = 0.9)) +
  scale_fill_manual(values = c("#999999", "#56B4E9", "#000000")) +
  theme(legend.justification=c(.5,.5), legend.position=c(.88,.88)) 

dev.off()


```

##Richness

```{r Plot}

#We can ask - Does habitat and wrack_length predict species richness?

# create a dataframe with just species data
spe_data <- sqrt(Wrack_Survey_Data_reduced[,-c(1:3)])
# create a dataframe with just factor data
trt_data <- Wrack_Survey_Data_reduced[,c(1:3)]

richness <- specnumber(spe_data)

#make new richness dataframe
richness.scores <- as.data.frame(richness)
richness.scores$habitat <- trt_data$habitat
richness.scores$wrack_num <- trt_data$wrack_num
richness.scores$wrack_length <- trt_data$wrack_length

#rename Habitats
levels(richness.scores$habitat)
levels(richness.scores$habitat) <- c("Abalone", "Tegula/Hermit") 

pdf(file = "Richness_wracksurvey_Jan2020SanNic.pdf", width = 6, height = 4, useDingbats=F)

Plot_richness <- ggplot(data=richness.scores,
                 aes(x=wrack_length, y=richness, 
                     colour = habitat)) +
  scale_colour_manual(name = "Habitat",
                      values=c("#000000", "#56B4E9")) +
  geom_point(size=2) 

Plot_richness + theme(axis.title.x = element_text(face="bold", size=22),
               axis.text.x  = element_text(size=20)) +
  ylab("Species Richness") +
 xlab("Wrack length (m)") +
  theme(axis.title.y = element_text(angle=90, 
                                    face="bold", 
                                   size=22, 
                                   vjust = 1),
        axis.text.y  = element_text(size=20)) +
  theme(legend.position="right") +
  #scale_y_continuous(expand = expand_scale(mult = c(0, 0)),
                   #  breaks = pretty(c(0,200), n = 5), 
                   #  limits = c(0,200)) +
  #scale_x_continuous(expand = expand_scale(mult = c(0, 0)),
                    # breaks = pretty(c(0,51), n = 5), 
                    # limits = c(0, 51)) +
  geom_smooth(method = lm)


dev.off()

```

```{r Model}

#We can ask - Does habitat and wrack_length predict species richness?

#test ANCOVA aassumption
model_richness<- lm(richness ~ wrack_length, 
                           data = richness.scores)
summary(model_richness)
anova(model_richness) #Richness and wrack-length are significant, which means wrack_length influences richness and does not meet assumptions of ANCOVA

#proceed with caution

#check normality assumptions
qqnorm(richness.scores$richness)
shapiro.test(richness.scores$richness) #non-normal
hist(richness.scores$richness)
leveneTest(richness ~ habitat, data = richness.scores) #not-equal

#Look at density plots to decide which models to test
hist <- ggplot(data=richness.scores,
                      aes(x=richness)) +
  #geom_histogram() +
  geom_density() +
  facet_grid(~habitat)
hist

model_richness_wrack <- glm(richness ~ wrack_length * habitat,
                       family=gaussian,
                       data=richness.scores)
summary(model_richness_wrack) 

car::Anova(model_richness_wrack) #use to pull our main effects


```


## Abundance

```{r line plot}

#We can ask does wrack length and habitat predict species abundance?

#use the long format data frame

#Sort by species
Wrack_Survey_Data_Ab <- Wrack_Survey_Data_long %>% 
  filter(Species == "Abalone") #remember you renamed levels in Plot section, so run again if this calls an error

Wrack_Survey_Data_Teg <- Wrack_Survey_Data_long %>% 
  filter(Species == "Tegula")

Wrack_Survey_Data_Herm <- Wrack_Survey_Data_long %>% 
  filter(Species == "Hermit")

#Subsitite each species to create 3 graphs
#check names of each one, stay consistent in case changes are made
#Ab = Abundance_Abalone_wracksurvey_Jan2020SanNic
#Teg = Abundance_Tegula_wracksurvey_Jan2020SanNic
#Herm = Abundance_Hermit_wracksurvey_Jan2020SanNic

pdf(file = "Abundance_Hermit_wracksurvey_Jan2020SanNic.pdf", width = 6, height = 4, useDingbats=F)

Plot_Her <- ggplot(data=Wrack_Survey_Data_Herm,
                 aes(x=wrack_length, y=Abundance, 
                     colour = habitat)) +
  scale_colour_manual(name = "Habitat",
                      values=c("#000000", "#56B4E9")) +
  geom_point(size=2) 

Plot_Her + theme(axis.title.x = element_text(face="bold", size=22),
               axis.text.x  = element_text(size=20)) +
  ylab("Hermit abundance") +
 xlab("Wrack length (m)") +
  theme(axis.title.y = element_text(angle=90, 
                                    face="bold", 
                                   size=22, 
                                   vjust = 1),
        axis.text.y  = element_text(size=20)) +
  theme(legend.position="right") +
  geom_smooth(method = lm)


dev.off()

```


```{r Model}

#For now - we are going to assume normality, but be conservative and use GLM. We need more data points before we pick a distribution and a model.

#Abalone

model_abundance_ab <- glm(Abundance ~ wrack_length * habitat,
                       family=gaussian,
                       data=Wrack_Survey_Data_Ab)
summary(model_abundance_ab) 
car::Anova(model_abundance_ab)

#Tegula

model_abundance_teg <- glm(Abundance ~ wrack_length * habitat,
                       family=gaussian,
                       data=Wrack_Survey_Data_Teg)
summary(model_abundance_teg) 
car::Anova(model_abundance_teg)

#Hermit

model_abundance_her <- glm(Abundance ~ wrack_length * habitat,
                       family=gaussian,
                       data=Wrack_Survey_Data_Herm)
summary(model_abundance_her) 
car::Anova(model_abundance_her)



```


```{r Boxplot}

pdf(file = "Habitat_v_wracklength_wracksurvey_Jan2020SanNic.pdf", width = 6, height = 4, useDingbats=F)

Plot_Box <- ggplot(data=Wrack_Survey_Data_long,
                      aes(y=wrack_length, x=habitat, fill = habitat)) +
  geom_boxplot() 

Plot_Box + 
  theme(axis.title.x = element_text(face="bold", size=22),
               axis.text.x  = element_text(size=20)) + 
  xlab("Habitat") +
  ylab("Wrack length (m)") +
  theme(axis.title.y = element_blank()) +
  theme(axis.title.y = element_text(angle=90, 
                                    face="bold", size=22,
                                    vjust=1.5),
        axis.text.y  = element_text(size=20)) +
   scale_fill_manual(values = c("#000000", "#56B4E9")) +
  theme(legend.title=element_blank()) +
  theme(legend.justification=c(.5,.5), legend.position=c(.15,.88)) 

dev.off()

```

#Abalone Surveys

```{r Data}

Abalone_Survey_Data <- read.csv("./Data/AbFocusedWrackSurveySNIJan2020.csv")

```

## On/Off

```{r Plot}

#create a dataframe with just important columns

Abalone_Survey_Data_reduced <- na.omit(Abalone_Survey_Data[, -c(1:5, 7)])

#Change to long format

Abalone_Survey_Data_long <- gather(data = Abalone_Survey_Data_reduced, 
                                 key = "Wrack.Use", value = "Abundance", ... 
                                 =  c(on_wrack, off_wrack), factor_key = TRUE)

#rename habitats
levels(Abalone_Survey_Data_long$habitat)
levels(Abalone_Survey_Data_long$habitat) <- c("Abalone", "Abalone/Urchin") 

#Barplot

meanAbundance_ab <- Abalone_Survey_Data_long %>% 
  group_by(habitat, Wrack.Use) %>% 
  summarize(mean_Abundance = mean(Abundance), SE = std.error(Abundance))

levels(meanAbundance_ab$Wrack.Use)
levels(meanAbundance_ab$Wrack.Use) <- c("On", "Off") 


pdf(file = "On.off_abalonesurvey_Jan2020SanNic.pdf", width = 6, height = 4, useDingbats=F)

Plot_Bar <- ggplot(data=meanAbundance_ab,
                      aes(y=mean_Abundance, 
                          x=habitat, 
                          fill = Wrack.Use)) +
  geom_bar(stat = "identity", colour = "black", 
           position = position_dodge(width = 0.9))

Plot_Bar + theme(axis.title.x = element_text(face="bold",
                                                 size=22),
                           axis.text.x  = element_text(size=20)) + 
  xlab("Habitat") +
  theme(axis.title.y = element_blank()) + 
  ylab("Count (out of 10)") +
  theme(axis.title.y = element_text(angle=90, 
                                    face="bold", 
                                    size=22, 
                                    vjust=1.5),
        axis.text.y  = element_text(size=20)) +
  geom_errorbar(aes(ymin=mean_Abundance - SE, 
                    ymax=mean_Abundance + SE), width = 0.05,
                position=position_dodge(width = 0.9)) +
  scale_fill_manual(name = "Wrack usage",
                    values = c("#999999", "#009E73")) +
  theme(legend.justification=c(.5,.5), legend.position=c(.18,.88)) +
  scale_y_continuous(expand = expand_scale(mult = c(0, 0)),
                     breaks = pretty(c(0,10), n = 5), 
                     limits = c(0,10))

dev.off()

```

```{r Model}

#For now - we are going to assume normality, but be conservative and use GLM. We need more data points before we pick a distribution and a model.

#check normality assumptions
qqnorm(Abalone_Survey_Data_long$Abundance)
shapiro.test(Abalone_Survey_Data_long$Abundance) #non-normal
hist(Abalone_Survey_Data_long$Abundance)
leveneTest(Abundance ~ habitat, data = Abalone_Survey_Data_long) #equal
leveneTest(Abundance ~ Wrack.Use, data = Abalone_Survey_Data_long) #equal

#Look at density plots to decide which models to test
hist <- ggplot(data=Abalone_Survey_Data_long,
                      aes(x=Abundance)) +
  #geom_histogram() +
  geom_density() +
  facet_grid(Wrack.Use~habitat)
hist

model_on.off <- glm(Abundance ~ Wrack.Use * habitat,
                       family=gaussian,
                       data=Abalone_Survey_Data_long)
summary(model_on.off) 
car::Anova(model_on.off)

```

#Grazer on/off

These transects were perpendicular to the water line. Therefore, they crossed many different habitats.

```{r Data}

Grazer_Survey_Data <- read.csv("./Data/GrzrOnOffSurveySNIJan2020.csv") 
# note this file has been edited and re-uploaded to Google drive, use the file that is most up to date
#edits were made to do repetitive data

#we want to remove any row that has double 0's, so a 0 for on and a 0 for off, this is because not every recorder recorded 0's when animals weren't seen. Therefore, by keeping double 0's in, we're inflating the likely hood of not finidng an animal

Grazer_Survey_Data_edited <- Grazer_Survey_Data %>% 
  mutate(Grazer_sum = on_wrack + off_wrack) %>% 
  filter(Grazer_sum != 0)
#this removed 13 observations

```

##On/Off

```{r Plot}

#create a dataframe with just important columns

Grazer_Survey_Data_reduced <- na.omit(Grazer_Survey_Data_edited[, -c(1:3, 5, 7)])

#Change to long format

Grazer_Survey_Data_long <- gather(data = Grazer_Survey_Data_reduced, 
                                 key = "Wrack.Use", value = "Abundance", ... 
                                 =  c(on_wrack, off_wrack), factor_key = TRUE)

#Barplot

meanAbundance_grazer <- Grazer_Survey_Data_long %>% 
  group_by(grzr_sp, Wrack.Use) %>% 
  summarize(mean_Abundance = mean(Abundance), SE = std.error(Abundance))

levels(meanAbundance_grazer$Wrack.Use)
levels(meanAbundance_grazer$Wrack.Use) <- c("On", "Off") 


pdf(file = "On.off_grazersurvey_Jan2020SanNic.pdf", width = 6, height = 4, useDingbats=F)

Plot_Bar_g <- ggplot(data=meanAbundance_grazer,
                      aes(y=mean_Abundance, 
                          x=grzr_sp, 
                          fill = Wrack.Use)) +
  geom_bar(stat = "identity", colour = "black", 
           position = position_dodge(width = 0.9))

Plot_Bar_g + theme(axis.title.x = element_text(face="bold",
                                                 size=22),
                           axis.text.x  = element_text(size=20)) + 
  xlab("Grazer") +
  theme(axis.title.y = element_blank()) + 
  ylab("Count (max 20)") +
  theme(axis.title.y = element_text(angle=90, 
                                    face="bold", 
                                    size=22, 
                                    vjust=1.5),
        axis.text.y  = element_text(size=20)) +
  geom_errorbar(aes(ymin=mean_Abundance - SE, 
                    ymax=mean_Abundance + SE), width = 0.05,
                position=position_dodge(width = 0.9)) +
  scale_fill_manual(name = "Wrack usage",
                    values = c("#999999", "#009E73")) +
  theme(legend.justification=c(.5,.5), legend.position=c(.18,.88)) +
  scale_y_continuous(expand = expand_scale(mult = c(0, 0)),
                     breaks = pretty(c(0,20), n = 5), 
                     limits = c(0,20))

dev.off()

#let's extract the sample sizes for each of the grazers bc we didn't see grazers everytime

Grazer_Survey_Data_reduced %>% 
  count(grzr_sp)


```


## Water distance

The tran_point_m represents the transect tape and roughly the distance from the water. 0m marks the furthest from the water (so we have to think of it in reverse)

We will look out grazer abundance x distance from water as a regression

```{r plot all}

levels(Grazer_Survey_Data_long$Wrack.Use)
levels(Grazer_Survey_Data_long$Wrack.Use) <- c("On", "Off") 

levels(Grazer_Survey_Data_long$grzr_sp)
levels(Grazer_Survey_Data_long$grzr_sp) <- c("Abalone", "Hermit", "Tegula", "Urchin") 

pdf(file = "Abundance_Distance_grazersurvey_Jan2020SanNic.pdf", width = 6, height = 4, useDingbats=F)

Plot_W <- ggplot(data=Grazer_Survey_Data_long,
                 aes(x=tran_point_m, y=Abundance, 
                     colour = grzr_sp)) +
  scale_colour_manual(name = "Grazer",
                    values = c("#000000", "#56B4E9", "#999999", "#009E73")) +
  geom_point(size=2, aes(shape = Wrack.Use)) 


Plot_W + theme(axis.title.x = element_text(face="bold", size=22),
               axis.text.x  = element_text(size=20)) +
  ylab("Count (max 20)") +
 xlab("Transect (m)") +
  theme(axis.title.y = element_text(angle=90, 
                                    face="bold", 
                                   size=22, 
                                   vjust = 1),
        axis.text.y  = element_text(size=20)) +
  theme(legend.position="right") +
  geom_smooth(method = lm)
  


dev.off()



```

```{r Model}

#We'll ignore wrack usage and first ask - does grazer abundance change with distance from waves?

#For now - we are going to assume normality, but be conservative and use GLM. We need more data points before we pick a distribution and a model.

#Visualize
qqnorm(Grazer_Survey_Data_long$Abundance)
#the distribution of this data appear logistic - where we really have either 0 or 20

#Look at density plots to decide which models to test
hist <- ggplot(data=Grazer_Survey_Data_long,
                      aes(x=Abundance)) +
  #geom_histogram() +
  geom_density() +
  facet_grid(~grzr_sp)
hist

model_grzer <- glm(Abundance ~ grzr_sp * tran_point_m,
                       family=binomial(),
                       data=Grazer_Survey_Data_long)
summary(model_on.off) 
car::Anova(model_on.off)

```

```{r Plot Prop}

#now we'll look at the proportion of on wrack to off wrack

Grazer_Survey_Data_prop <- Grazer_Survey_Data_reduced %>% 
  mutate(prop.on = on_wrack/off_wrack)

levels(Grazer_Survey_Data_prop$grzr_sp)
levels(Grazer_Survey_Data_prop$grzr_sp) <- c("Abalone", "Hermit", "Tegula", "Urchin") 

pdf(file = "Abundance_Distance_on_grazersurvey_Jan2020SanNic.pdf", width = 6, height = 4, useDingbats=F)

Plot_W <- ggplot(data=Grazer_Survey_Data_prop,
                 aes(x=tran_point_m, y=prop.on, 
                     colour = grzr_sp)) +
  scale_colour_manual(name = "Grazer",
                    values = c("#000000", "#56B4E9", "#999999", "#009E73")) +
  geom_point(size=2) 


Plot_W + theme(axis.title.x = element_text(face="bold", size=22),
               axis.text.x  = element_text(size=20)) +
  ylab("Proportion on wrack") +
 xlab("Transect (m)") +
  theme(axis.title.y = element_text(angle=90, 
                                    face="bold", 
                                   size=22, 
                                   vjust = 1),
        axis.text.y  = element_text(size=20)) +
  theme(legend.position="right") +
  scale_y_continuous(expand = expand_scale(mult = c(0, 0)),
                     breaks = pretty(c(0,2), n = 5), 
                     limits = c(0,2))
  


dev.off()





```



# Invasive Wrack

This the invasive wrack survey, where we surveyed wrack patties for sargassum

```{r Data}

Invasive_Survey_Data <- read.csv("./Data/InvasiveWrackSurveySNIJan2020.csv") 

```

```{r Size}

#Let's first look at the size of wrack patties that is invasive for each site

levels(Invasive_Survey_Data$site)
levels(Invasive_Survey_Data$site) <- c("Cosign", "West Marker Poles") 

pdf(file = "Wracksize_invasviewracksurvey_Jan2020SanNic.pdf", width = 6, height = 4, useDingbats=F)

Plot_Box <- ggplot(data=Invasive_Survey_Data,
                      aes(y=ellipse_A_m2, x=site, fill = site)) +
  geom_boxplot() 

Plot_Box + 
  theme(axis.title.x = element_text(face="bold", size=22),
               axis.text.x  = element_text(size=20)) + 
  xlab("Site") +
  ylab("Wrack area (m2)") +
  theme(axis.title.y = element_blank()) +
  theme(axis.title.y = element_text(angle=90, 
                                    face="bold", size=22,
                                    vjust=1.5),
        axis.text.y  = element_text(size=20)) +
   scale_fill_manual(values = c("#999999", "#009E73")) +
    theme(legend.position="none")

dev.off()

t.test(ellipse_A_m2 ~ site, data = Invasive_Survey_Data)



```

```{r Percent}

#Now we'll ask - what percent of patties have invasive sargassum?

#we're going to use a pie chart *GROSS* but i can't think of another way to visualize this

#first we have to find the total no's and total yes's

Pie_data <- Invasive_Survey_Data %>% 
  group_by(site) %>% 
  count(invasive)

levels(Pie_data$invasive)
levels(Pie_data$invasive) <- c("absent", "present") 


#Make a piechart for each site

Pie_data_Cosign <- Pie_data %>% 
  filter(site == "Cosign")

Pie_data_WMP <- Pie_data %>% 
  filter(site == "West Marker Poles")

pdf(file = "piechart_cosign_invasviewracksurvey_Jan2020SanNic.pdf", width = 6, height = 4, useDingbats=F)

ggplot(Pie_data_Cosign, aes(x="", y=n, fill=invasive)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() +
  scale_fill_manual(name = "Invasive",
                    values = c("#333333", "#999999"))

dev.off()

pdf(file = "piechart_wmp_invasviewracksurvey_Jan2020SanNic.pdf", width = 6, height = 4, useDingbats=F)

ggplot(Pie_data_WMP, aes(x="", y=n, fill=invasive)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() +
  scale_fill_manual(name = "Invasive",
                    values = c("#333333", "#009E73"))

dev.off()


```


```{r Invasive}

#We'll ask - Of the patties that have invasive wrack, what percent is invasive?

#we'll remove patties with 0 invasvie wrack

Patty_invasive <- Invasive_Survey_Data %>% 
  filter(percent > 0)


pdf(file = "Proportion_invasviewracksurvey_Jan2020SanNic.pdf", width = 6, height = 4, useDingbats=F)

Plot_Box_2 <- ggplot(data=Patty_invasive,
                      aes(y=percent, x=site, fill = site)) +
  geom_boxplot() 

Plot_Box_2 + 
  theme(axis.title.x = element_text(face="bold", size=22),
               axis.text.x  = element_text(size=20)) + 
  xlab("Site") +
  ylab("Percent invasive (%) ") +
  theme(axis.title.y = element_blank()) +
  theme(axis.title.y = element_text(angle=90, 
                                    face="bold", size=22,
                                    vjust=1.5),
        axis.text.y  = element_text(size=20)) +
   scale_fill_manual(values = c("#999999", "#009E73")) +
  theme(legend.position="none")

dev.off()

t.test(percent ~ site, data = Patty_invasive)



```

# Consumption Experiment

```{r Data} 

Experiment_Data <- read.csv("./Data/SNICosignJan2020.csv") 

```


## Exp. 1

```{r Data}

#we'll clean up the file for just experiment 1 and add 2 new columns that we'll use later

Experiment_1_Data <- Experiment_Data %>% 
  filter(experiment == "1A" | experiment == "1B") %>% 
  filter(treatment != "ABX") %>% #remove abalone exclusion
  filter(!is.na(Wf)) %>% #remove NAs from Wf
  mutate(consumption = Wf/Time) %>% #I made a new column called time in excel prior to calling the file into R, this gives us g/day
  mutate(Total_animals = X0.5m_herm + X0.5m_teg + X0.5m_ab + 
           X0.5m_ur + X0.5m_pac + X0.5m_chi + X0.5m_lim) %>% 
  mutate(On_plate = herm_on_plate + teg_on_plate + ab_on_plate)

```

```{r Plot}

# First we'll visualize the data using a bar plot - Do grazers prefer sargassum or macro?

levels(Experiment_1_Data$algae_spp.)
levels(Experiment_1_Data$algae_spp.) <- c("Macrocystis", "Sargassum") 

#Barplot

meanconsumption_data <- Experiment_1_Data %>% 
  group_by(algae_spp.) %>% 
  summarize(mean_consumption = mean(consumption), SE = std.error(consumption))


pdf(file = "Exp1_bar_Jan2020SanNic.pdf", width = 6, height = 4, useDingbats=F)

Plot_Bar <- ggplot(data=meanconsumption_data,
                      aes(y=mean_consumption, 
                          x=algae_spp., 
                          fill = algae_spp.)) +
  geom_bar(stat = "identity", colour = "black", 
           position = position_dodge(width = 0.9))

Plot_Bar + theme(axis.title.x = element_text(face="bold",
                                                 size=22),
                           axis.text.x  = element_text(size=20)) + 
  xlab("Algae species") +
  theme(axis.title.y = element_blank()) + 
  ylab("Consumption (g/day)") +
  theme(axis.title.y = element_text(angle=90, 
                                    face="bold", 
                                    size=22, 
                                    vjust=1.5),
        axis.text.y  = element_text(size=20)) +
  geom_errorbar(aes(ymin=mean_consumption - SE, 
                    ymax=mean_consumption + SE), width = 0.05,
                position=position_dodge(width = 0.9)) +
  scale_fill_manual(name = "Algae species",
                    values = c("#CC9966", "#FF9999")) +
  theme(legend.position="none")

dev.off()

#boxplot

pdf(file = "Exp1_box_Jan2020SanNic.pdf", width = 6, height = 4, useDingbats=F)

Plot_Box <- ggplot(data=Experiment_1_Data,
                      aes(y=consumption, x=algae_spp., fill = algae_spp.)) +
  geom_boxplot() 

Plot_Box + 
  theme(axis.title.x = element_text(face="bold", size=22),
               axis.text.x  = element_text(size=20)) + 
  xlab("Algae Species") +
  ylab("Consumption (g/day)") +
  theme(axis.title.y = element_blank()) +
  theme(axis.title.y = element_text(angle=90, 
                                    face="bold", size=22,
                                    vjust=1.5),
        axis.text.y  = element_text(size=20)) +
   scale_fill_manual(name = "Algae species",
                    values = c("#CC9966", "#FF9999")) +
  theme(legend.position="none")

dev.off()


```

```{r LMEM}

#http://bbolker.github.io/mixedmodels-misc/glmmFAQ.html#model-specification

#We're going to fun Linear Mixed Effect Models because we want to make block a random factor - there could be variation in block that is driving the patterns in consumption

#package - lme4
#use lmer for gaussian - normal distributions
#use glmr for other distributions

#in this case we want to make Block a random effect

######test distributions

#normal
qqnorm(Experiment_1_Data$consumption)
shapiro.test(Experiment_1_Data$consumption) #non-normal 
hist(Experiment_1_Data$consumption)
leveneTest(consumption ~ algae_spp., data = Experiment_1_Data) #nequal

#Look at density plots to decide which models to test
ggplot(data=Experiment_1_Data, aes(x=consumption)) +
  #geom_histogram() +
  geom_density() +
  facet_grid( ~ algae_spp.) #very not-normal

#proceed with caustion

Exp1_model <- lmer(consumption ~ algae_spp.
                       + (1 | block),
                data = Experiment_1_Data)

car::Anova(Exp1_model)

post.hoc.Exp1 <-glht(Exp1_model, linfct = mcp(algae_spp. = "Tukey"))
cld(post.hoc.Exp1)

```

```{r Animal}

#we're going to see if the total number of animals explains consumption

#first, we'll add a new column which will be the proportion of M:S consumed

#we have to go from the long format to the wide format

Experiment_1_Data_reduced <- na.omit(Experiment_1_Data[, -c(1:2, 4:6, 8:27, 31)])
  
Experiment_1_Data_wide <- spread(Experiment_1_Data_reduced, algae_spp., consumption)
Experiment_1_Data_wide

Experiment_1_Data_wide <- Experiment_1_Data_wide %>% 
  mutate(prop.consump = Macrocystis/Sargassum)


pdf(file = "Exp1_Animal_v_consumption_Jan2020SanNic.pdf", width = 6, height = 4, useDingbats=F)

Plot_prop <- ggplot(data=Experiment_1_Data_wide,
                 aes(x=Total_animals, y=prop.consump)) +
  geom_point(size=2) 

Plot_prop + theme(axis.title.x = element_text(face="bold", size=12),
               axis.text.x  = element_text(size=10)) +
  ylab("Macrocystis to Sargassum consumption") +
 xlab("Total animals counted") +
  theme(axis.title.y = element_text(angle=90, 
                                    face="bold", 
                                   size=12, 
                                   vjust = 1),
        axis.text.y  = element_text(size=10)) +
  theme(legend.position="right") +
  geom_smooth(method = lm)


dev.off()

Animal.model <- lm(prop.consump ~ Total_animals, data = Experiment_1_Data_wide)
summary(Animal.model)


```

```{r Spe. Dis.}

#now let's see what species make up this habitat - i.e. what are the grazers that could be eating our plates

#we need to take the observations and turn them into long format

Experiment_1_Data_long <- gather(data = Experiment_1_Data, 
                                 key = "Species.sighted", 
                            value = "Abundance.sighted", ... 
                                 =  c(X0.5m_herm,
                                      X0.5m_teg,
                                      X0.5m_ab,
                                      X0.5m_ur,
                                      X0.5m_pac,
                                      X0.5m_chi,
                                      X0.5m_lim), factor_key = TRUE)

levels(Experiment_1_Data_long$Species.sighted)
levels(Experiment_1_Data_long$Species.sighted) <- c("Hermit", "Tegula", "Abalone", "Urchin", "Pachygrapsus", "Chiton", "Limpet") 


pdf(file = "Exp1_box_animalspec_Jan2020SanNic.pdf", width = 6, height = 4, useDingbats=F)

Plot_Box_1 <- ggplot(data=Experiment_1_Data_long,
                      aes(y=Abundance.sighted, x=Species.sighted, 
                          fill = Species.sighted)) +
  geom_boxplot() 

Plot_Box_1 + 
  theme(axis.title.x = element_text(face="bold", size=22),
               axis.text.x  = element_text(size=20, angle = 45, hjust = 1)) + 
  xlab("Animal") +
  ylab("# counted") +
  theme(axis.title.y = element_blank()) +
  theme(axis.title.y = element_text(angle=90, 
                                    face="bold", size=22,
                                    vjust=1.5),
        axis.text.y  = element_text(size=20)) +
  scale_fill_manual(name = "Animals",
                     values = c("#56B4E9", #Hermit
                                "#999999", #Tegula
                                "#000000", #Abalone
                                "#009E73", #Urchin
                                "#0072B2", #Pachy
                                "#D55E00", #Chiton
                                "#CC79A7")) +
  theme(legend.position="none")

dev.off()



```


## Exp. 2

```{r Data}

#we'll clean up the file for just experiment 2 and add 2 new columns that we'll use later

Experiment_2_Data <- Experiment_Data %>% 
  filter(experiment == "2A" | experiment == "2B") %>% 
  filter(!is.na(Wf)) %>% #remove NAs from Wf
  mutate(consumption = Wf/Time) %>% #I made a new column called time in excel prior to calling the file into R, this gives us g/day
  mutate(Total_animals = X0.5m_herm + X0.5m_teg + X0.5m_ab + 
           X0.5m_ur + X0.5m_pac + X0.5m_chi + X0.5m_lim)

#let's get sample for each habitat

Experiment_2_Data_n <- Experiment_2_Data %>% 
  count(trt)

```

```{r Plot}

levels(Experiment_2_Data$algae_spp.)
levels(Experiment_2_Data$algae_spp.) <- c("Macrocystis", "Sargassum") 

levels(Experiment_2_Data$trt)
levels(Experiment_2_Data$trt) <- c("Abalone", "Abalone", "Ab/Urch", "Hermit", "Teg/Hermit") 
Experiment_2_Data$trt <- factor(Experiment_2_Data$trt, levels = c("Ab/Urch", "Abalone", "Hermit", "Teg/Hermit"))

#negative consumption typically isn't real, so we'll change negatives to 0

Experiment_2_Data$consumption[Experiment_2_Data$consumption <0] <- 0

#boxplot

pdf(file = "Exp2_box_Jan2020SanNic.pdf", width = 6, height = 4, useDingbats=F)

Plot_Box <- ggplot(data=Experiment_2_Data,
                      aes(y=consumption, x=trt, fill = algae_spp.)) +
  geom_boxplot() 

Plot_Box + 
  theme(axis.title.x = element_text(face="bold", size=22),
               axis.text.x  = element_text(size=20)) + 
  xlab("Habitat") +
  ylab("Consumption (g/day)") +
  theme(axis.title.y = element_blank()) +
  theme(axis.title.y = element_text(angle=90, 
                                    face="bold", size=22,
                                    vjust=1.5),
        axis.text.y  = element_text(size=20)) +
   scale_fill_manual(name = "Algae species",
                    values = c("#CC9966", "#FF9999")) +
  theme(legend.justification=c(.5,.5), legend.position=c(.88,.88)) +
  scale_y_continuous(expand = expand_scale(mult = c(0, 0)),
                     breaks = pretty(c(0,25), n = 5), 
                     limits = c(0,25))

dev.off()


```

```{r LMEM}

Exp2_model <- lmer(consumption ~ algae_spp. * trt
                       + (1 | block),
                data = Experiment_2_Data)

car::Anova(Exp2_model)

post.hoc.Exp2 <-glht(Exp2_model, linfct = mcp(algae_spp. = "Tukey"))
cld(post.hoc.Exp2)


```

```{r Animal}

#we're going to see if the total number of animals explains consumption

#first, we'll add a new column which will be the proportion of M:S consumed

#we have to go from the long format to the wide format

Experiment_2_Data_reduced <- na.omit(Experiment_2_Data[, -c(1:2, 5:6, 8:27)])
  
Experiment_2_Data_wide <- spread(Experiment_2_Data_reduced, algae_spp., consumption)
Experiment_2_Data_wide

Experiment_2_Data_wide <- Experiment_2_Data_wide %>% 
  mutate(prop.consump = Macrocystis/Sargassum)

#there are 4 outliers, greater than 2000 So we're going to remove them 

Experiment_2_Data_wide_removed <- Experiment_2_Data_wide %>% 
  filter(prop.consump < 25)


pdf(file = "Exp2_Animal_v_consumption_Jan2020SanNic.pdf", width = 6, height = 4, useDingbats=F)

Plot_prop <- ggplot(data=Experiment_2_Data_wide_removed,
                 aes(x=Total_animals, y=prop.consump,
                     colour = trt)) +
  scale_colour_manual(name = "Habitat",
                      values=c("#009E73", "#000000", "#56B4E9", "#999999")) +
  geom_point(size=2) 

Plot_prop + theme(axis.title.x = element_text(face="bold", size=12),
               axis.text.x  = element_text(size=10)) +
  ylab("Macrocystis to Sargassum consumption") +
 xlab("Total animals counted") +
  theme(axis.title.y = element_text(angle=90, 
                                    face="bold", 
                                   size=12, 
                                   vjust = 1),
        axis.text.y  = element_text(size=10)) +
  theme(legend.position="right") #+
  #geom_smooth(method = lm)


dev.off()

Animal.model <- lm(prop.consump ~ Total_animals, data = Experiment_1_Data_wide)
summary(Animal.model)

#this figure is really wack, so it seems the proportion isn't the best way to visualize this data - So let's try to look at this with Macro on one axis and Sarg on the other axis - so a regression + a heat map of total animals counted


#Heat Map

Experiment_2_Data_wide_heat <- Experiment_2_Data_wide %>% 
  mutate(consumption_M = Macrocystis/Time) %>% 
  mutate(consumption_S = Sargassum/Time) # we have to adjust for time again

library(RColorBrewer)

pdf(file = "AnimalvMvS.pdf", width = 6, height = 4, useDingbats=F)

ggplot(Experiment_2_Data_wide_heat, aes(x =consumption_S, y = consumption_M, 
                                   z = Total_animals)) + 
  geom_tile() +
  stat_summary_2d() +
  scale_fill_distiller(name = "Total animals counted", palette = "PRGn") +
  geom_point(shape = 1, col = 'white') +
 theme(axis.title.x = element_text(face="bold",
                                                 size=18),
               axis.text.x  = element_text(size=14)) + 
  xlab("Sargassum (g/day)") +
  #theme(axis.title.y = element_blank()) + 
  ylab("Macrocystis (g/day)") +
  theme(axis.title.y = element_text(angle=90, 
                                    face="bold", 
                                  size=18, 
                                    vjust=1.5),
        axis.text.y  = element_text(size=14)) +
   theme(axis.text.y  = element_text(size=14),
        axis.text.x = element_text(size=14)) +
  theme(legend.position="right") 


dev.off()


```


```{r Spe. Dis.}

#now let's see what species make up this habitat - i.e. what are the grazers that could be eating our plates

#we need to take the observations and turn them into long format

Experiment_2_Data_long <- gather(data = Experiment_2_Data, 
                                 key = "Species.sighted", 
                            value = "Abundance.sighted", ... 
                                 =  c(X0.5m_herm,
                                      X0.5m_teg,
                                      X0.5m_ab,
                                      X0.5m_ur,
                                      X0.5m_pac,
                                      X0.5m_chi,
                                      X0.5m_lim), factor_key = TRUE)

levels(Experiment_2_Data_long$Species.sighted)
levels(Experiment_2_Data_long$Species.sighted) <- c("Hermit", "Tegula", "Abalone", "Urchin", "Pachygrapsus", "Chiton", "Limpet") 


pdf(file = "Exp2_box_animalspec_Jan2020SanNic.pdf", width = 6, height = 4, useDingbats=F)

Plot_Box_2 <- ggplot(data=Experiment_2_Data_long,
                      aes(y=Abundance.sighted, x=trt, 
                          fill = Species.sighted)) +
  geom_boxplot() 

Plot_Box_2 + 
  theme(axis.title.x = element_text(face="bold", size=16),
               axis.text.x  = element_text(size=14, angle = 45, hjust = 1)) + 
  xlab("Habitat") +
  ylab("# counted") +
  theme(axis.title.y = element_blank()) +
  theme(axis.title.y = element_text(angle=90, 
                                    face="bold", size=16,
                                    vjust=1.5),
        axis.text.y  = element_text(size=14)) +
   scale_fill_manual(name = "Animals",
                     values = c("#56B4E9", #Hermit
                                "#999999", #Tegula
                                "#000000", #Abalone
                                "#009E73", #Urchin
                                "#0072B2", #Pachy
                                "#D55E00", #Chiton
                                "#CC79A7")) + #Limpet
  theme(legend.position="none")

dev.off()

```


## Elevation

We can look at how relative elevation effects consumption and varies with habitat. We will use the auto-level column to compare relative elevation between blocks. We can NOT get absolute elevation from this data.



```{r Data}

Elevation_Data <- read.csv("./Data/ElevationSurveySNI2020.csv") 


```

###Exp.1

```{r Cons v Elevation}

# We will first combine dataframes so we can look at elevation and consumption

Experiment_1_Data_wide #use this dataframe from above
str(Experiment_1_Data_wide) #block is a factor

Elevation_Data_filter <- Elevation_Data %>% 
  select(experiment, trt, block, auto_level.m.) %>% 
  filter(experiment == "1A" | experiment == "1B")
str(Elevation_Data_filter) #block is an integer

Elevation_Data_filter$block <- factor(Elevation_Data_filter$block, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15"))


Elevation_Data_Exp1 <- 
  left_join(Experiment_1_Data_wide, Elevation_Data_filter, 
            by = c("block")) #join datasets by block

#Heat Map

Elevation_Data_Exp1_heat <- Elevation_Data_Exp1 %>% 
  mutate(consumption_M = Macrocystis/Time) %>% 
  mutate(consumption_S = Sargassum/Time) # we have to adjust for time again

library(RColorBrewer)

pdf(file = "ElevationvMvS_Exp1.pdf", width = 6, height = 4, useDingbats=F)

ggplot(Elevation_Data_Exp1_heat, aes(x =consumption_S, y = consumption_M, 
                                   z = auto_level.m.)) + 
  geom_tile() +
  stat_summary_2d() +
  scale_fill_distiller(name = "Relative elevation (m)", palette = "PRGn") +
  geom_point(shape = 1, col = 'white') +
 theme(axis.title.x = element_text(face="bold",
                                                 size=18),
               axis.text.x  = element_text(size=14)) + 
  xlab("Sargassum (g/day)") +
  #theme(axis.title.y = element_blank()) + 
  ylab("Macrocystis (g/day)") +
  theme(axis.title.y = element_text(angle=90, 
                                    face="bold", 
                                  size=18, 
                                    vjust=1.5),
        axis.text.y  = element_text(size=14)) +
   theme(axis.text.y  = element_text(size=14),
        axis.text.x = element_text(size=14)) +
  theme(legend.position="right") 


dev.off()


```

```{r Animals v Elevation}

pdf(file = "Exp1_Animal_v_elevation_Jan2020SanNic.pdf", width = 6, height = 4, useDingbats=F)

Plot_ele <- ggplot(data=Elevation_Data_Exp1_heat,
                 aes(x=Total_animals, y=auto_level.m.)) +
  geom_point(size=2) 

Plot_ele + theme(axis.title.x = element_text(face="bold", size=12),
               axis.text.x  = element_text(size=10)) +
  ylab("Relative elevation (m)") +
 xlab("Total animals counted") +
  theme(axis.title.y = element_text(angle=90, 
                                    face="bold", 
                                   size=12, 
                                   vjust = 1),
        axis.text.y  = element_text(size=10)) +
  theme(legend.position="right") +
  geom_smooth(method = lm)


dev.off()

Animal.model_2 <- lm(auto_level.m. ~ Total_animals, data = Elevation_Data_Exp1_heat)
summary(Animal.model_2)



```

###Exp.2

```{r Cons v Elevation}

# We will first combine dataframes so we can look at elevation and consumption

Experiment_2_Data_wide #use this dataframe from above
str(Experiment_2_Data_wide) #block is a factor

Elevation_Data_filter_2 <- Elevation_Data %>% 
  select(experiment, trt, block_let, auto_level.m.) %>% 
  filter(experiment == "2A" | experiment == "2B")
str(Elevation_Data_filter_2) #block is an integer

Elevation_Data_Exp2 <- 
  left_join(Experiment_2_Data_wide, Elevation_Data_filter_2, 
            by = c("block" = "block_let")) #join datasets by block

#Heat Map

Elevation_Data_Exp2_heat <- Elevation_Data_Exp2 %>% 
  mutate(consumption_M = Macrocystis/Time) %>% 
  mutate(consumption_S = Sargassum/Time) # we have to adjust for time again

library(RColorBrewer)

pdf(file = "ElevationvMvS_Exp2.pdf", width = 6, height = 4, useDingbats=F)

ggplot(Elevation_Data_Exp2_heat, aes(x =consumption_S, y = consumption_M, 
                                   z = auto_level.m.)) + 
  geom_tile() +
  stat_summary_2d() +
  scale_fill_distiller(name = "Relative elevation (m)", palette = "PRGn") +
  geom_point(shape = 1, col = 'white') +
 theme(axis.title.x = element_text(face="bold",
                                                 size=18),
               axis.text.x  = element_text(size=14)) + 
  xlab("Sargassum (g/day)") +
  #theme(axis.title.y = element_blank()) + 
  ylab("Macrocystis (g/day)") +
  theme(axis.title.y = element_text(angle=90, 
                                    face="bold", 
                                  size=18, 
                                    vjust=1.5),
        axis.text.y  = element_text(size=14)) +
   theme(axis.text.y  = element_text(size=14),
        axis.text.x = element_text(size=14)) +
  theme(legend.position="right") 


dev.off()


```

```{r Animals v Elevation}

pdf(file = "Exp2_Animal_v_elevation_Jan2020SanNic.pdf", width = 6, height = 4, useDingbats=F)

Plot_ele <- ggplot(data=Elevation_Data_Exp2_heat,
                 aes(x=Total_animals, y=auto_level.m.,
                     colour = trt.x)) +
  scale_colour_manual(name = "Habitat",
                      values=c("#009E73", "#000000", "#56B4E9", "#999999")) +
  geom_point(size=2) 


Plot_ele + theme(axis.title.x = element_text(face="bold", size=12),
               axis.text.x  = element_text(size=10)) +
  ylab("Relative elevation (m)") +
 xlab("Total animals counted") +
  theme(axis.title.y = element_text(angle=90, 
                                    face="bold", 
                                   size=12, 
                                   vjust = 1),
        axis.text.y  = element_text(size=10)) +
  theme(legend.position="right") +
  geom_smooth(method = lm)


dev.off()

qqnorm(Elevation_Data_Exp2_heat$auto_level.m.)
shapiro.test(Elevation_Data_Exp2_heat$auto_level.m.) #non-normal 
hist(Elevation_Data_Exp2_heat$auto_level.m.)
leveneTest(auto_level.m. ~ trt.x, data = Elevation_Data_Exp2_heat) #unequal

#Look at density plots to decide which models to test
ggplot(data=Elevation_Data_Exp2_heat, aes(x=auto_level.m.)) +
  #geom_histogram() +
  geom_density() +
  facet_grid( ~ trt.x) 

Exp2_model_ele <- lm(auto_level.m. ~ trt.x * Total_animals,
                       #+ (1 | block),
                data = Elevation_Data_Exp2_heat)

car::Anova(Exp2_model_ele)

post.hoc.Exp2_ele <-glht(Exp2_model_ele, linfct = mcp(trt.x = "Tukey"))
cld(post.hoc.Exp2_ele)


```

```{r Habitat}

#Lets look out the average elevation per habitat

pdf(file = "Elevation_v_habitat_Jan2020SanNic.pdf", width = 6, height = 4, useDingbats=F)

Plot_Box_hab <- ggplot(data=Elevation_Data_Exp2_heat,
                      aes(y=auto_level.m., x=trt.x, 
                          fill = trt.x)) +
  geom_boxplot() 

Plot_Box_hab + 
  theme(axis.title.x = element_text(face="bold", size=16),
               axis.text.x  = element_text(size=14, angle = 45, hjust = 1)) + 
  xlab("Habitat") +
  ylab("Relative elevation (m)") +
  theme(axis.title.y = element_blank()) +
  theme(axis.title.y = element_text(angle=90, 
                                    face="bold", size=16,
                                    vjust=1.5),
        axis.text.y  = element_text(size=14)) +
   scale_fill_manual(name = "Habitat",
                     values = c("#009E73",
                                "#000000",
                                "#56B4E9", 
                                "#999999")) + 
  theme(legend.position="none")

dev.off()



```

##Compare

We're going to compare elevation across experients in order to compare 'abalone' habitats

```{r Ele}

Elevation_Data_filter <- Elevation_Data %>% 
  filter(trt != "NA")

levels(Elevation_Data_filter$trt)
levels(Elevation_Data_filter$trt) <- c("Abalone.exp2", "Abalone.exp1", "Ab/Urch", "Hermit", "Teg/Hermit") 
Elevation_Data_filter$trt <- factor(Elevation_Data_filter$trt, levels = c("Ab/Urch", "Abalone.exp1", "Abalone.exp2","Hermit", "Teg/Hermit"))

pdf(file = "Elevation_v_habitat_compare_Jan2020SanNic.pdf", width = 6, height = 4, useDingbats=F)

Plot_Box_hab <- ggplot(data=Elevation_Data_filter,
                      aes(y=auto_level.m., x=trt, 
                          fill = trt)) +
  geom_boxplot() 

Plot_Box_hab + 
  theme(axis.title.x = element_text(face="bold", size=16),
               axis.text.x  = element_text(size=14, angle = 45, hjust = 1)) + 
  xlab("Habitat") +
  ylab("Relative elevation (m)") +
  theme(axis.title.y = element_blank()) +
  theme(axis.title.y = element_text(angle=90, 
                                    face="bold", size=16,
                                    vjust=1.5),
        axis.text.y  = element_text(size=14)) +
   scale_fill_manual(name = "Habitat",
                     values = c("#009E73",
                                "#D55E00",
                                "#000000",
                                "#56B4E9", 
                                "#999999")) + 
  theme(legend.position="none")

dev.off()






```

#Feb 2019

Consummption experiment at SNI in Feb 2019

```{r data}

SNI_Feb_Data <- read.csv("./Data/SNIFeb2019Cosign.csv") 

```

```{r Plot}

#We decided that pools and crevices are the same, so we're going to relabel them

levels(SNI_Feb_Data$habitat)
levels(SNI_Feb_Data$habitat) <- c("Crevice/Pool", "Emergent", "Crevice/Pool") 

pdf(file = "Box_Feb2019SanNic.pdf", width = 6, height = 4, useDingbats=F)

Plot_Box <- ggplot(data=SNI_Feb_Data,
                      aes(y=adjustedweight, x=bench, fill = habitat)) +
  geom_boxplot() 

Plot_Box + 
  theme(axis.title.x = element_text(face="bold", size=22),
               axis.text.x  = element_text(size=20)) + 
  xlab("Bench") +
  ylab("Consumption (g/day)") + #experiments were only out 1 day
  theme(axis.title.y = element_blank()) +
  theme(axis.title.y = element_text(angle=90, 
                                    face="bold", size=22,
                                    vjust=1.5),
        axis.text.y  = element_text(size=20)) +
   scale_fill_manual(name = "Substrate",
                    values = c("#999999", "#009E73")) +
  theme(legend.justification=c(.5,.5), legend.position=c(.88,.88)) #+
  #scale_y_continuous(expand = expand_scale(mult = c(0, 0)),
                    # breaks = pretty(c(0,25), n = 5), 
                     #limits = c(0,25))

dev.off()


```

```{r Model}

#normal
qqnorm(SNI_Feb_Data$adjustedweight)
shapiro.test(SNI_Feb_Data$adjustedweight) #non-normal 
hist(SNI_Feb_Data$adjustedweight)
leveneTest(adjustedweight ~ bench, data = SNI_Feb_Data) #unequal
leveneTest(adjustedweight ~ habitat, data = SNI_Feb_Data) #equal

#Look at density plots to decide which models to test
ggplot(data=SNI_Feb_Data, aes(x=adjustedweight)) +
  #geom_histogram() +
  geom_density() +
  facet_grid(habitat ~ bench) #very not-normal

#proceed with caustion

Feb_model <- glm(adjustedweight ~ habitat * bench,
                      family = gaussian,
                data = SNI_Feb_Data)

car::Anova(Feb_model)



```

